\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Samantha}{Yuhan}{
\href{mailto:syuhan@berkeley.edu}{syuhan@berkeley.edu} | 949.836.7611
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{UC Berkeley}
\descript{Data Science}
\location{May 2021 | Berkeley, CA}
\location{ GPA: 3.5 }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://facebook/sammmmmn}{\bf sammmmmn} \\
Github:// \href{https://github.com/samyuhan}{\bf samyuhan} \\
LinkedIn://  \href{https://www.linkedin.com/in/samanthayuhan}{\bf samanthayuhan} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Principles and Techniques of Data Science \\
Linear Algebra \\
Designing Information Devices and Systems I \\
Data Structures \\
Program Structures \\
Foundations of Data Science \\
Calculus \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Python \textbullet{} Java \textbullet{} Javascript \\
SQL \textbullet{} HTML \textbullet{} CSS \textbullet{} JavaScript \\ 
Tableau \textbullet{} Pandas \textbullet{} Jupyter Notebook \\
Excel \textbullet{} Scheme \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
Drawing/Painting \\
Graphic Design \\
Netflix \\
Shopping \\
Reading \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{MobilityWare}
\descript{| Software Engineer/Data Analytics Intern }
\location{June 2018 - Aug 2018 | Irvine, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Built ETL (Extract, Transform, Load) processes using SQL and SSIS (SQL Server) to transform granular data into organized data structures.
\item Implemented a model output process in Python to feed data into the NLP model responsible for classifying user inputs and parsing through advertisement data, allowing for 70 percent increase in model efficiency.
\item Combined the model outputs and player advertisement interaction data to create a player to genre relational table, helping the company distinguish advertisement patterns and revise their marketing strategy to increase click-through rate.
\end{tightemize}
\sectionsep

\runsubsection{UC Berkeley Division of Data Sciences}
\descript{| Curriculum Developer }
\location{Aug 2018 – Present | Berkeley, CA}
\begin{tightemize}
\item Worked closely with UC Berkeley faculty to design open-source materials for lectures, labs, and homework and taught students face-to-face in classrooms and office hours.
\item Developed curriculum materials (homework, labs, lectures) in Jupyter notebooks to implement data science principles, specifically for Introduction to Human Physiology. 
\end{tightemize}
\sectionsep

\runsubsection{Opportunity Through Data}
\descript{| Development Board Member}
\location{Sept 2018 – Present | Berkeley, CA}
\begin{tightemize}
\item Taught women in minimum security prisons technical skills to prepare them for data science careers, thus reducing recidivism. Piloting our program at the Federal Correctional Institution Dublin.
\item Designed a 12 week data science education program as well as assignments to teach Python and statistics.
\item Reached out to partner with stakeholders to set up professional development workshops and mentorship.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXTRACURRICULAR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extracurricular}
\runsubsection{Undergraduate Laboratory at Berkeley}
\descript{| Undergraduate Researcher for Advanced Technologies Group }
\location{Sept 2018 – Present | Berkeley, CA}
\begin{tightemize}
\item Applied electroencephalography to analyze occipital lobe activation and used machine learning model development with matplotlib, numpy, and scikit-learn.
\item Built web pages for data visualization (web development with Mindful Project).
\item Found correlations between data columns and displayed results on a webpage using Flask and Learn.
\end{tightemize}
\sectionsep

\runsubsection{Innovative Design}
\descript{| Graphic Design Team Member}
\location{Sept 2018 – Present | Berkeley, CA}
\begin{tightemize}
\item Provide pro-bono designs for flyers, banners, logos, websites, and more for organizations to support the student and local community. (Design using Adobe Illustrator and Photoshop)
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
