%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{verbatim}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Theodore Shiao}{ \urlstyle{same}\href{theo.shiao.me}{theo.shiao.me} \textbullet{}
\href{mailto:theo.shiao@berkeley.edu}{theo.shiao@berkeley.edu} \textbullet{}
(310) 691-4061
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of \\California, Berkeley}
\descript{BA in Computer Science, B.S. in Business Administration}
\location{May 2021 | Berkeley, CA}
\location{ Cum. GPA: 3.67 / 4.0}
\location{ SAT: 2370}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/theoshiao}{\bf theoshiao} \\
LinkedIn://  \href{https://www.linkedin.com/in/theodoreshiao}{\bf theodoreshiao}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Efficient Algorithms and Intractable Problems \\
Data Structures \\
Structure and Interpretation \\of Computer Programs \\
Computer Architecture (Machine Structures) \\
Discrete Mathematics and Probability Theory \\
Foundations of Data Science \\
Principles of Business \\
Microeconomic Theory \\
Linear Algebra \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Proficient:}
Java \textbullet{}   Python \textbullet{} Swift \textbullet{} C \\

\location{Familiar:}
HTML \textbullet{} CSS \textbullet{} JavaScript \textbullet{} \LaTeX
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
Basketball (Go Lakers!)\\
Hip Hop\\
Travel\\
Food\\
Kayaking\\
Rock Climbing


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\begin{comment}
\runsubsection{IMPD}
\descript{| Intern }
\location{September 2018 - Present | Berkeley, CA}
\begin{tightemize}
\vspace{\topsep}
\item Worked on Project ATMA (Artificial Tragedy Monitor and Autoresponder), an artificial intelligence platform that can recognize emergency situations and automatically call 911 through real-time analysis of video footage. 
\item Found and input videos to train the platform to recognize emergency and distress signals in video footage.
\item Building a Deep Neural Network with Keras API.
\end{tightemize}
\sectionsep
\end{comment}

\runsubsection{Wayfair}
\descript{| Incoming Product Management Intern }
\location{June 2019 | Boston, MA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\\
\sectionsep

\runsubsection{CoolJamm}
\descript{| Software Engineering Intern }
\location{August 2018 - December 2018 | Berkeley, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Helped with a background music sharing platform that includes personalized suggestions and AI-generated music
\item Created a back-end tool that automatically verifies the copyright status of music in the database against YouTube's ContentID system.
\item Automated song uploading process using the YouTube API.
\item Developed front-end using Angular CLI for controlling testing tools, with various inputs to sort, restrict, and change testing parameters.
\end{tightemize}
\sectionsep

\begin{comment}
\runsubsection{Cambi}
\descript{| Software Engineering Intern}
\location{September 2018 - December 2018 | Berkeley, CA}
\begin{tightemize}
\item Worked on adding features and streamlining their application by making the UI more intuitive in XCode.
\item Changed the viewing screens to allow users to see more relevant information regarding cards at once.
\end{tightemize}
\sectionsep
\end{comment}

\runsubsection{Upsync}
\descript{| Data Analytics Consultant }
\location{September 2017 – December 2018 | Berkeley, CA}
\begin{tightemize}
\item Organized a Virtual Reality Hackathon and Speaker Panel with speakers from Google, Oculus, and HTC.
\item Created a website for one of our clients.
\item Responsible for growing and managing Upsync's \$2000 budget through investment theses and portfolio allocations.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{SwiftJump iOS}
\descript{| Swift}
Created an iOS vertical scrolling platforming game using SpriteKit in Swift. Includes randomized level designs, various power-ups, and character customization.

\sectionsep

\runsubsection{Yelp Review Predictor}
\descript{| Python}
Wrote a program that estimates the Yelp rating of a review based off the words used in the review. Worked with the Apache Spark library to create a Naive Bayes classifier for the Yelp dataset. 
\sectionsep

\runsubsection{NBA Stock Market}
\descript{| Python, JavaScript, HTML, CSS}
Created a web application that acted as a NBA stock market, where users had the ability to buy/ sell NBA player 'stock' (five game running average of fantasy score). Hosted in Flask, with Python back-end used to pull NBA player data and calculate stock values and JavaScript front-end. 
\sectionsep

\begin{comment}
\runsubsection{Shape from Stereo}
\descript{| C}
Created a program that produces a displacement map of an image given two input images. Simulates depth perception by comparing the differences between the two images. Also implemented quadtree compression for bitmap images.
\end{comment}

\runsubsection{Berkeley Maps}
\descript{| Java}
Programmed the back-end of a web-mapping application of the Berkeley area. Created and implemented the routing algorithm to determine shortest-paths with the Open Street Map dataset. Also included a rasterer for zooming functionality. 
\sectionsep


\begin{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2014	     & top 52/2500  & KPCB Engineering Fellow\\
2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
2013	     & National  & Jump Trading Challenge Finalist\\
2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
\end{tabular}
\sectionsep
\end{comment}

\end{minipage} 
\end{document}  \documentclass[]{article}
